Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
wordings

%------------------------------------
\subsection{On the stability considering effects of implementation issues and quantisation noises}
\label{sec:stability}
%------------------------------------

In order to obtain a sound synthesis of the digital controller, the effect
of FWL implementation in controller and quantisation noises in closed loop
system have to be considered.  Considering that the quantiser $Q1$ is the
source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise
$\nu_{2}$, the following equation is written for the system in
Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties
$\Delta \vec{G}$ and the FWL effects on controller ($\hat{C}(z)$):
%
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
%
that can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
%
where
%
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
%
and
%
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantisation step \cite{astrom1997computer}, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantisation step of  ADC and DAC.
% 
\end{myassumption}

@@

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for
synthesis of digital controllers able to stabilize closed loop system,
considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$),
quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital
controllers.  Based on it, the model for plant uncertainty due quantisation
noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions
on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise
is bounded.  The quantisation noise is indeed bounded, since the following
assumption~\ref{whitenoise}.

>>>>

%------------------------------------
\subsection{Stability under FWL and Noise}
\label{sec:stability}
%------------------------------------

Correct synthesis of the digital controller requires consideration of the
effect of FWL in controller and quantisation noises in the closed loop
system.  Let the quantiser $Q1$ be the source of a white noise $\nu_{1}$ and
$Q2$ be the source of a white noise $\nu_{2}$.  The following equation
models the system in Figure~\ref{fig:sampledsystem}, encompassing the
parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
the controller ($\hat{C}(z)$):
%
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
%
The above can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
%
where
%
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
%
and
%
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)}.
\end{equation}

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
uncorrelated white noises and their amplitudes are always bounded by the
half of quantisation step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
where $q_{1}$ and $q_{2}$, respectively, are the quantisation steps of ADC
and DAC.
% 
\end{myassumption}

@@

Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for the
ability of a digital controller to stabilize the closed loop system,
considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
software.  Based on it, the model for plant uncertainty due quantisation
noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
Lemma~\ref{lemma:eq_int_stab} are satisfied and if the quantisation noise is
bounded.  The boundedness of the quantisation noise is
assumption~\ref{whitenoise}.
